%label:"art:symplectoAndHamiltonian"
%author:JeffHicks
%name:"Symplectomorphisms and Hamiltonian isotopies "
%type:"article"

In previous definitions, we've presented 
\begin{itemize}
    \item some diffeomorphic spaces (i.e. $T^*T^n$ and $(\CC^*)^n$) which should be considered the same as symplectic manifolds.
    \item some spaces which are diffeomorphic (i.e. $S^2$ and itself) which can be equipped with clearly different symplectic structures (i.e. $\text{vol}_g$ and $\text{vol}_{2g}$).
\end{itemize} 
We now introduce an equivalence relation for symplectic structures on a manifold.
\input{def_symplectomorphism}
One property of the canonical symplectic structure on the cotangent bundle $T^*Q$ is that the symplectomorphism type of $T^*Q$ is only dependent on the diffeomorphism type of $Q$ \cite{da2001lectures}.
Let $f: Q_1\to Q_2$ be a diffeomorphism. 
Define the \emph{lift} of $f$ to be a map $f_\#: T^*Q_1\to T^* Q_2$ defined by
\[f_\#(q,p)=(f(q),  ((df_q)^*)^{-1}p\]
The lift plays well with the tautological 1-form, in the sense that if $\lambda_i$ is the tautological 1-form for $T^*Q_i$, then $(f_\#)^*\lambda_2=\lambda_1$. 
    

A particularly interesting type of symplectomorphism is one which arises as an isotopy. A symplectic isotopy is a smooth 1-parameter family of maps $\phi_t: X\times I\to X$ which for fixed values of $t$ give a symplectomorphism, and start at the identity (in the sense that $\phi_0=\operatorname{id}_X$). 
These are examples of smooth isotopies and so they can equivalently be described as the flow of a time-dependent vector field.
\input{def_flow}
There is an equivalence between vector fields and flows.
\input{thm_existenceOfFlow}
One can check that a smooth isotopy $\phi_t$ is a symplectic isotopy by verifying that the symplectic form is preserved by the infinitesimal generator $V_t$.
This yields an easy to check criterion.
\input{prp_exactSymplecticHamiltonian}
\begin{proof}
    We prove the forward direction, using that $\phi^*_t\omega=\omega$ for all $t$.
    By taking the derivative with respect to $t$ of both sides, we obtain:
\begin{align*}
    0=&\frac{d}{dt}\phi^*\omega
    =\phi^*_t\mathcal L_{V_t}\omega
\end{align*}
Since $\phi$ is a diffeomorphism,  this is equivalent to the vanishing of $\mathcal L_{V_t}\omega$, 
\begin{align*}
 0=& \mathcal L_{V_t}\omega
\end{align*}
Applying Cartan's formula, and using that $\omega$ is closed,
\begin{align*}
0=&d(\iota_{V_t}\omega)+ \iota_{V_t}(d\omega)=d(\iota_{V_t}\omega).
\end{align*}
This means that $\iota_{V_t}\omega$ is closed.
\end{proof}
One could ask for the stronger condition of exactness for the 1-form $\iota_{V_t}\omega$.
In this case, we can describe vector field $V_t$ by a function on $X$. 
\input{def_hamiltonianVectorField}
The uniqueness of this vector field arises from the non-degeneracy of the symplectic form $\omega$.
This additionally means that to every exact symplectic isotopy we can associate a generating Hamiltonian function.
The Hamiltonian isotopies give a large set of easy-to-describe symplectic isotopies, and the relation between Hamiltonian isotopies and all symplectic isotopies has a nice interpretation in terms of the topology of $X$. 
\begin{corollary}
    If $H^1(X,  \RR)=0$,  then every symplectic isotopy is Hamiltonian. 
\end{corollary}
\input{exm_hamiltonsEquations}
A notable feature of Hamiltonian flow $V_H$ is that it preserves the level sets of $H$, as 
\[V_H(H)=dH(V_H)=\omega(V_H, V_H)=0.\]
\input{exm_sphereRotation}
The Hamiltonian flow is sometimes called the symplectic gradient. 
In the setting where we have a compatible triple $(X, \omega,g, J)$, the Hamiltonian flow and gradient are related by the almost complex structure. 
\input{lem_gradients}
\begin{proof}
    This is a direct computation. On any test vector $v$,
    \begin{align*}
        g(J V_H, v)=\omega(V_H, v)=dH(v)= g(\grad(H), v)
    \end{align*}
    Because $g$ is nondegenerate, $\grad(H)=JV_H$. 
\end{proof}