%tag:000U
%label:"art:lagrangianSurgery"
%author:JeffHicks
%name:"surgery of Lagrangian submanifolds "
%type:"article"

We will now look at some ways to glue together new Lagrangian submanifolds from old.
A source of inspiration for us will be from smooth topology, where tools such as surgery, Morse theory, and cobordisms provide methods for generating new manifolds.
An example where we can take a method from topology and directly import it into symplectic geometry is connect sum for Lagrangian curves inside of surfaces.
In this setting, two Lagrangian curves which intersect at a point are modified at the point of intersection to produce a connected Lagrangian submanifold.
See \cref{fig:connectsumcurve}.

The Polterovich connect sum is a generalization of this surgery to higher dimensions, which smooths out a transverse intersection between two Lagrangian submanifolds. 
The idea of construction is to first use \cref{lemma:straightening} to provide a canonical neighborhood for a transverse Lagrangian intersection, then construct a model neck in that canonical neighborhood. 
\input{fig_polterovichSurgery}
\input{prp_polterovichSurgery}
\input{prf_polterovichSurgery}
One feature of surgery is that it does not uniquely specify a Lagrangian --- different choices of curves $\gamma$ produce different Lagrangian submanifolds.
Recall that to a Lagrangian isotopy $\li_t: L\to C$ we associate a cohomology class $\Flux_{\li_t}\in H^1(L)$. 
We can similarly associate a flux class to a Lagrangian surgery.
A given surgery profile curve $\gamma$ can be extended to a family of Lagrangian surgery profiles by scaling the profile curve by a parameter $s$.  
This gives us a family of surgeries $L_1\#_{s\gamma} L_2$, which are Lagrangian isotopic.
The flux of the surgery is defined to be the flux of this isotopy. 
\input{prp_fluxOfSurgery}
As a result, we will write $L_1\#_{\lambda}L_2$ for a curve where the profile curve $\gamma$, real axis and imaginary axis bound a region of area $\lambda$. 

The order of the summands plays an important role in Lagrangian surgery, as it is generally the case that $L_1\#L_2$ and $L_2\#L_1$ are not Lagrangian isotopic. 
\input{exm_polterovichSurgery}



Now that we have a geometric description of $L_1\#_\lambda L_2$, we discuss what object it represents in the Fukaya category. We restrict ourselves to $\dim_\CC(X)=1$ so that we may draw pictures (but the construction works in higher dimensions as well).

Let $L_0$ be some test Lagrangian, which intersects both $L_1$ and $L_2$ as in \cref{fig:roundingCorner}. If the surgery neck is chosen to lie in a neighborhood disjoint from the intersections  $L_0\cap (L_1\cup L_2)$, then these intersections are in bijection with the intersections $L_0\cap (L_1\# L_2)$.
\input{fig_roundingCorner}
 The intuition from \cite{fukaya2007lagrangian} is that there is a bijection between certain holomorphic triangle with boundary on $L_0, L_1, L_2$ which passes through the intersection point $p_{12}$, and holomorphic strips with boundary on $L_0$ and $L_1\# L_2$. Since holomorphic triangles contribute to the $\emprod^3$ structure coefficients, and strips to the differential, it is reasonable to hope that we can state a relation between $L_1, L_2,$ and $L_1\#L_2$ as objects of the Fukaya category.


First, we observe that the intersection point $p_{12}$ determines a morphism in $\hom(L_2, L_1)$. Since we've assumed that $L_1$ and $L_2$ intersect at only one point, we know that $\emprod^1(p_{12})=0$. We can therefore form the twisted complex $\cone(p_{12})$. We now provide justification for why this is isomorphic to $L_1\# L_2$.

We have already observed that for our test Lagrangian $L_0$ we had an isomorphism of vector spaces between $\hom(L_0, L_1)\oplus \hom(L_0, L_2)$ and $\hom(L_0, L_1\#_{p_{12}}L_2)$. The differential on $\hom(L_0, L_1\#_{p_{12}}L_2)$ comes counting holomorphic strips, which we break into two types: those which avoid a neighborhood of the surgery neck, and those which pass through the surgery neck. 
\input{prp_stripsInLagrangianSurgery}
The more difficult portion is to understand the strips which pass through the neck.
\input{thm_roundingCorner}
From this we obtain the following corollary
\input{cor_surgeryExactTriangle}
