%label:"art:examplesOfLagrangianSubmanifolds"
%type:"article"
%name:"examples of Lagrangian submanifolds"

For symplectic surfaces, we have a complete classification of the Lagrangian submanifolds. 
\input{exm_curvelagrangian}
Some Lagrangian submanifolds can be constructed easily from Lagrangian submanifolds in lower dimensions.
\input{exm_productTorus}
We will later see that  $T^*Q$ gives a local model of a symplectic manifold. For this reason, Lagrangian submanifolds of $T^*Q$  serve as local models for Lagrangian submanifolds in general $X$.
\input{exm_lagrangianInCotangent}
\input{prf_lagrangianInCotangent}
In the setting of cotangent bundles we can also build local models for the intersections of Lagrangian submanifolds.
\input{exm_lagrangiansFromConormals}
In these notes, we will attempt to shed a little light on the construction and classification of Lagrangian submanifolds. 
Even in the simplest examples, this classification can become quite difficult. 
To give a meaningful answer to this question, we'll need a notion of equivalence between Lagrangian submanifolds. 
For submanifolds, a natural equivalence to consider is the isotopy class or the homotopy class.

Let $\li_t: L\times I\to X$ be a homotopy of Lagrangian submanifolds.
We now describe the \emph{flux class} of the homotopy, which is an element $\Flux_{\li_t}\in H^1(L;\RR)$.
To define this class we prescribe its values on chains of $L$. 
Let $c\in C_1(L)$ be a chain. 
Then the homotopy can be applied to $c$ to give a 2-chain $\li_t(c)\in C_2(X)$. 
\input{def_flux}
To show that this is a cohomology class, we need to show that the flux homomorphism $\Flux_{\li_t}$ vanishes on boundaries $\partial b\in C_1(L_0)$ 

Without loss of generality, suppose that $I=[0,1]$, and let $b\in C_2(L)$ be a 2-chain.
Then $\li_t(b)$ similarly gives a 3-chain in $X$ whose boundary components satisfy the relation $\li_t(\partial b)=i_0(b)-i_1(b)+\partial(\li_t(b))$. 
Applying the definition of the flux homomorphism to this relation yields:
\[
    \Flux_{\li_t}(\partial b)=\int_{\li_t(\partial b)}\omega=\int_{i_0(b)}\omega-\int_{i_1(b)}\omega + \int_{\partial(\li_t(b))}\omega\]
The first two terms vanish because $i_0(b)$ and $i_1(b)$ are subsets of a Lagrangian submanifold so $\omega|_{\li_0(L)}=\omega|_{\li_1(L)}=0$.
Because $\omega$ is closed, an application of Stoke's theorem shows that the last term vanishes as well. 
\input{exm_fluxInCylinder}
\input{fig_fluxInCylinder}
\input{exm_fluxInCotangent}
This example highlights two important properties of Lagrangian submanifolds, and Lagrangian homotopy. 
First, there homotopies a stronger notion of equivalence for Lagrangian submanifolds beyond homotopy by looking at those homotopies which sweep out zero flux. 
\input{def_exactHomotopy}
Similar to \cref{claim:exactsymplectichamiltonian}, exact isotopies of Lagrangian submanifolds can be characterized in terms of the Lagrangian isotopy itself. 
\input{clm_hamiltonianFlux}
\input{prf_hamiltonianFlux}
This shows that when $L$ is embedded, a time dependent Hamiltonian $H_t: L\times (-\epsilon, \epsilon)\to \RR$ defines an isotopy of embeddings $\li_t: L\times(-\epsilon, \epsilon)\to X$ for small values of $t$.
We say this is the isotopy generated by the Hamiltonian $H$.
Provided that $L$ is compact, we immediately get the following statement on the non-displacibility of Lagrangian submanifolds by small exact Lagrangian homotopies. 
\input{prp_lagrangianIntersection}
\input{prf_lagrangianIntersection}
In fact, this can extends to the case of time-dependent Hamiltonians for sufficiently small $t$. 
\begin{corollary}
    Let $H_t: L\to \RR$ generate a Hamiltonian isotopy. 
    Then there exists $\epsilon>0$ such that for all $t_0, t_1\in [0,\epsilon)$, 
    \[|\li_{t_0}(L)\cap \li_{t_1}(L)|\geq \sum_{i=1}^n b_i(L).\]
\end{corollary}
Secondly, every cohomological class is realizable as a flux class in the cotangent bundle. 
This observation motivates the following theorem, which shows that this behavior occurs more generally.
\input{thm_weinsteinNeighborhood}
In other words,  a symplectic neighborhood of a Lagrangian submanifold is determined by the diffeomorphism class of the Lagrangian. 
This local model will be useful later, as many of our constructions involving Lagrangian submanifolds will involve restricting to a Weinstein neighborhood, performing the construction there, and then implanting our construction into the original symplectic manifold.
An example of such a construction is the following.
\input{lem_straightening}
\input{prf_straightening}

\input{exr_coordinateFreeClosedLagrangian}
\input{exr_noLagSphereInCP2}
\input{exr_hamiltonianFlux}

\input{exr_gluingconormals}
\input{exr_polterovichSurgery}
\input{exr_hamiltonianIsotopyInCotangentBundle}
\input{exr_lagrangianIntersectionsAreCritPoints}
\input{exr_diplacibilityOnS2}
