%label:"art:maximumPrinciples"
%author:JeffHicks
%name:"maximum principles"
%type:"exposition"
We recall some of the basics of Hamiltonian Floer theory. Let $X$ be a compact symplectic manifold. 
Given $H_t: X\times \RR\to \RR$ a time dependent Hamiltonian, we obtain an action on the free loop space
\input{eqn_floerAction}
whose critical points are the time one periodic orbits of $V_{H_t}$. Given a $\omega$-compatible almost complex structure, we observe that cylinders $u: \RR_s\times S^1_t\to X$ which satisfy the $H_t$ perturbed Floer equation
\input{eqn_floerEquation}
parameterize the negative gradient flow lines of $A_{H_t}$. For curves $\gamma_+, \gamma_-$, let $\mathcal M(\gamma_+, \gamma_-)$ denote the moduli space of solutions to Floer's equation with ends limiting to $\gamma_+, \gamma_-$.
Supposing that $X$ is an exact symplectic manifold, and that our time-dependent Hamiltonian is chosen in a generically, the Floer cochains $\CF(X, H_t)$ are the graded vector space generated  on the time one orbits of $H_t$.
We take a slightly different convention (following Equation 5.2 of \cite{abouzaid2010geometric}) and give each orbit the grading $\deg(\gamma)=n-CZ(\gamma)$, where $CZ(\gamma)$ is the Conley-Zehnder index.
The structure coefficients of the differential are given by counts of solutions to Floer's equation. The theory becomes powerful when it satisfies the following properties:
\begin{itemize}
    \item $\CF(X, H_t)$ is a chain complex. The key step is to show that when $\dim(\mathcal M(\gamma_+, \gamma_-))=1$, there exists a compactification of this moduli space by including broken cylinders. A compactification of the space comes from applying Gromov compactness, while additional requirements on $X$ are sometimes required ensure that the only configurations which appear in the compactification are broken cylinders. In our setting, the only breaking configurations which may occur are broken cylinders, as $X$ is exact (so $\omega(\pi_2(X))=0)$.
    \item Given $H_{t, 0}$ and $H_{t, 1}$ two time-dependent Hamiltonians, there exists a continuation map $\CF(X, H_{t, 0})\to \CF(X, H_{t, 1})$. Furthermore, this map is a homotopy equivalence. 
    \item Finally, we need some way to compute $\CF(X, H_{t, 1})$. One way to do this is to observe that for $C^2$ small Hamiltonians the Floer cochains agree with the Morse cochains (and only consist of constant orbits). By either using the PSS-isomorphism or by analyzing Floer trajectories, the Floer cohomology can be compared to the Morse cohomology of $X$.
\end{itemize}
The major difference in defining the Hamiltonian Floer cohomology for Liouville domains $X$ (as opposed to compact symplectic manifolds) comes from the proof of Gromov-compactness. The first step in the proof of Gromov-compactness is to apply Arzel\'a-Ascoli to out sequence of pseudoholomorphic maps.  Because $\hat X$ is not compact, we cannot apply the Arzel\'a-Ascoli theorem to a sequence of pseudoholomorphic cylinders $u: S^1\times \RR \to \hat X$. 

We now give an example of where we can solve the issue of non-compactness.
\input{exm_compactnessFromMaximumModulus}
In order to extend \cref{exm:compactnessFromMaximumModulus} to the setting of $\hat X$, we will use the maximum principle. First, we will need to assume that we have chosen our almost complex structure for $\hat X$ so that the sub-bundle spanned by the vector fields $\partial_r, R$ form an almost complex subspace.
\input{def_contactTypeACS}
We will also need to assume that we have chosen our Hamiltonian so that over the symplectization it only depends on the $r$-coordinate.
For such a contact type almost complex structure and Hamiltonian there exists a version of \cref{exm:compactnessFromMaximumModulus}.
\input{prp_liouvilleIsGeometricallyBounded}
\input{prf_liouvilleIsGeometricallyBounded}