%label:"con:polterovichSurgery"
%author:JeffHicks
%name:"Lagrangian connect sum "
%type:"construction"

We will now look at some ways to glue together new Lagrangian submanifolds from old.
A source of inspiration for us will be from smooth topology, where tools such as surgery, Morse theory, and cobordisms provide methods for generating new manifolds.
An example where we can take a method from topology and directly import it into symplectic geometry is connect sum for Lagrangian curves inside of surfaces.
In this setting, two Lagrangian curves which intersect at a point are modified at the point of intersection to produce a connected Lagrangian submanifold.
See \cref{fig:polterovichSurgery}.

The Polterovich connect sum is a generalization of this surgery to higher dimensions, which smooths out a transverse intersection between two Lagrangian submanifolds. 
The idea of construction is to take a  \snip{standard model for the transverse intersection}{lemma:straightening}, then construct a model neck in that canonical neighborhood. 
\input{fig_polterovichSurgery}
\input{prp_polterovichSurgery}
\input{prf_polterovichSurgery}
The order of the summands plays an important role in Lagrangian surgery, as rarely are the Lagrangian $L_1\#L_2$ and $L_2\#L_1$ isotopic. 

The surgery construction does not uniquely specify \emph{the} Lagrangian surgery of two Lagrangian submanifolds,  different choices of curves $\gamma$ produce different Lagrangian submanifolds.
Given a Lagrangian isotopy $\li_t: L\to C$ we associate \snip{flux cohomology class}{def:flux} $\Flux_{\li_t}\in H^1(L)$. 
We can similarly associate a flux class to a Lagrangian surgery.
A given surgery profile curve $\gamma$ can be extended to a family of Lagrangian surgery profiles by scaling the profile curve by a parameter $s$.  
This gives us a family of surgeries $L_1\#_{s\gamma} L_2$, which are Lagrangian isotopic.
The flux of the surgery is defined to be the flux of this isotopy. 
\input{prp_fluxOfSurgery}
The flux of $\gamma$ is the area bounded by $\gamma$ and the two axis. This is sometimes called the width or neck-width of the surgery.
We will write $L_1\#_{\lambda}L_2$ a Lagrangian connect sum determined by a surgery profile curve with flux $\lambda$.

\input{exm_polterovichSurgery}

